\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-07 projects/project_5/molecular_dynamics/article/article.tex
Writing introduction

\section{Introduction}
\label{sec:introduction}
    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. It is based on the simple
    idea of considering a finite number of molecules and letting them interact
    for a fixed amount of time, which gives us an idea of how the system
    evolves.

@@

\begin{thebibliography}{9}
\bibitem{min_image}
    \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention}
\bibitem{equipar}
    \url{https://en.wikipedia.org/wiki/Equipartition\_theorem}
\bibitem{virial}
    \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
\label{sec:introduction}
    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. Some of the more pioneering
    works in molecular dynamics are often found in the study of chemical
    physics and more specifically proteins.  In 1975, Levitt and Warshel
    \cite{folding} simulated protein folding and in 1976 Cooper
    \cite{thermoprotein} presented results on thermodynamic fluctuations in
    protein folding with methods comparable to todays standards.

    In order to verify the molecular dynamics model one can for instance
    compare with physical experiments. For molecular systems one particular
    method is of special interest, namely nuclear magnetic resonance
    spectroscopy.

    Molecular Dynamics can take on many forms. Notable in the addition of what
    we examine in this project, is the Monte-Carlo and Brownian dynamics
    variants of MD.

    It is based on the simple idea of considering a finite number of molecules
    and letting them interact for a fixed amount of time, which gives us an
    idea of how the system evolves.

@@

\section{Conclusion}
\label{sec:conclusion}

\begin{thebibliography}{9}
\bibitem{folding}
    Levitt, M., \& Warshel, A., `Computer simulation of protein folding`, Nature, Vol. 253, No. 5494. Available from: \url{http://csb.stanford.edu/levitt/Levitt_NAT75_folding.pdf}
\bibitem{thermoprotein}
    Cooper, A. `Thermodynamic fluctuations in protein molecules`, Proceedings of the National Academy of Sciences of the United States of America, Vol. 73, No. 8. Available from: \url{http://www.pnas.org/content/73/8/2740.full.pdf}
\bibitem{min_image}
    \url{https://en.wikipedia.org/wiki/Periodic_boundary_conditions#Practical_implementation:_continuity_and_the_minimum_image_convention}
\bibitem{equipar} \url{https://en.wikipedia.org/wiki/Equipartition\_theorem}
\bibitem{virial} \url{https://en.wikipedia.org/wiki/Virial_theorem}
\end{thebibliography}
\end{document}
